---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# regex4impala

The goal of regex4impala is to write regular expression in impala.

## Installation

You can install the released version of regex4impala from [CRAN](https://CRAN.R-project.org) with:

```{r eval=F}
install.packages("regex4impala")
```

You can install the released version of add2md from [Github](https://github.com/JiaxiangBU/add2md) with:

```{r eval=F}
devtools::install_github('JiaxiangBU/regex4impala')
```

```{r eval=F}
library(regex4impala)
```


## Example

Considered in the plan.

***

Please note that the 'regex4impala' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

